\section{Introduction} \label{sec:intro}
\textit{Warning: If the reader happens to be unfamiliar with the show} Game of Thrones\textit{, he shall be warned for this paper is dark and full of spoilers.}\\

\noindent
\textit{"When you play a game of thrones you win or you die."}\\
- Cersei Lannister in \got\\
by George R. R. Martin \citep{martin1996a}\\

The iconic TV show \got{}
is characterized by its range of main characters as well as its unneglectable disposition to also have these main characters killed. Not only does the show count more than 150 characters that appear at least three times in the first books, it has more than half of these (63\%) dead by the end of season 7. Most characters' main motive is to gain power and by that to sit on the iron throne. Their willingness to become the ruler of the seven kingdoms, regardless of other people's lives, is the story told in \got.\\
This paper will examine the characters from the very first book and season as well as their relationships among each other. Will these constellations give away an estimate for who will die in season 7 or who could potentially rule the seven kingdoms? As season one mostly is based on the first book \got, the show and the book are treated equally. The few connections of the first season to the second book \textit{A Clash of Kings} \citep{martin1998a} have been neglected for this paper.\\
As \got{} is a commonly researched area for network analysis \citep{beniwal_network_2018, glander_another_2018, networkofthrones_networks_2017}, this paper contributes to the discussion by taking positive and negative relationships between the characters into account. As the show is based on a dense network of allegiances and enemies, characters with the same amount of connections might face completely opposite challenges and threats depending on the amount of support and aversion targeted towards them. Furthermore, dead characters are given special priority in this paper. If said character with numerous connections mostly faces negative attitudes towards him or her, it could be more likely for him or her to die earlier. Hence, this paper will examine this connection of relationship quality and death or power in \got.